\input texinfo   @c -*-texinfo-*-
@c %**start of header
@setfilename control.info
@settitle Octave Control Systems Package
@afourpaper
@set VERSION 2.3.54
@finalout
@c @afourwide
@c %**end of header


@c The following macro is used for the on-line help system, but we don't
@c want lots of `See also: foo, bar, and baz' strings cluttering the
@c printed manual (that information should be in the supporting text for
@c each group of functions and variables).

@macro seealso {args}
@iftex
@vskip 2pt
@end iftex
@ifnottex
@c Texinfo @sp should work but in practice produces ugly results for HTML.
@c A simple blank line produces the correct behavior. 
@c @sp 1

@end ifnottex
@noindent
@strong{See also:} \args\.
@end macro


@c %*** Start of TITLEPAGE
@titlepage
@title control @value{VERSION}
@subtitle Control Systems Package for GNU Octave
@author Lukas F. Reichlin
@page
@vskip 0pt plus 1filll
Copyright @copyright{} 2009-2012, Lukas F. Reichlin @email{lukas.reichlin@@gmail.com}

This manual is generated automatically from the texinfo help strings
of the package's functions.

Permission is granted to make and distribute verbatim copies of
this manual provided the copyright notice and this permission notice
are preserved on all copies.

Permission is granted to copy and distribute modified versions of this
manual under the conditions for verbatim copying, provided that the entire
resulting derived work is distributed under the terms of a permission
notice identical to this one.

Permission is granted to copy and distribute translations of this manual
into another language, under the same conditions as for modified versions.
@page
@chapheading Preface
The @acronym{GNU} Octave control package from version 2 onwards was
developed by Lukas F. Reichlin and is based on the proven open-source
library @acronym{SLICOT}. This new package is intended as a replacement
for control-1.0.11 by A. Scottedward Hodel and his students.
Its main features are:
@itemize
@item Reliable solvers for Lyapunov, Sylvester and algebraic Riccati equations.
@item Pole placement techniques as well as @tex $ H_2 $ @end tex
and @tex $ H_{\infty} $ @end tex
synthesis methods.
@item Frequency-weighted model and controller reduction.
@item System identification by subspace methods.
@item Overloaded operators due to the use of classes introduced with Octave 3.2.
@item Support for descriptor state-space models and non-proper transfer functions.
@item Improved @acronym{MATLAB} compatibility.
@end itemize

@sp 5
@subheading Acknowledgments
The author is indebted to several people and institutions who helped
him to achieve his goals. I am particularly grateful to Luca Favatella
who introduced me to Octave development as well as discussed and revised
my early draft code with great patience. My continued support from the
@acronym{FHNW} University of Applied Sciences Northwestern Switzerland,
where I could work on the control package as a semester project, has also
been important. Furthermore, I thank the @acronym{SLICOT} authors
Peter Benner, Vasile Sima and Andras Varga for their advice.
Finally, I appreciate the feedback, bug reports and patches I have received
from various people. The names of all contributors should be listed in the
@acronym{NEWS} file.


@sp 5
@subheading Using the help function
Some functions of the control package are listed with a leading @code{@@lti/}.
This is only needed to view the help text of the function, e.g. @w{@code{help norm}}
shows the built-in function while @w{@code{help @@lti/norm}} shows the overloaded
function for @acronym{LTI} systems. Note that there are @acronym{LTI} functions
like @code{pole} that have no built-in equivalent.

When just using the function, the leading @code{@@lti/} must @strong{not} be typed.
Octave selects the right function automatically. So one can type @w{@code{norm (sys, inf)}}
and @w{@code{norm (matrix, inf)}} regardless of the class of the argument.
@end titlepage
@c %*** End of TITLEPAGE

@contents
@c @chapter Function Reference
@include functions.texi

@end
@bye
